Deciding to Disclose: Pregnancy and Alcohol Misuse

### 2014-07-04 Abstract.tex
Added acknowledgements
Added tex  root for easier building
Sketching abstract

\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax

@@

>>>>

%!TEX root = disclosure_game.tex
\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax

@@

Background:
Roots in agents, decision theory, game theory.
We draw together methodologies from game theory, agent based modelling, and decision theory to explore the process of decision making around disclosure. This is framed in the context of pregnant women disclosing their drinking behaviour to their midwives.

Objective: 
To pimp out this method, and maybe get some insight into reality.
Address the perceived ad hoc character with strongly theoretically underpinned agents.

Methods: 
Made a game, made a simulation, did a sensitivity analysis.

Results: 
Look! Chaos! Look! Qualitative trends! Look! More data needed.

Conclusions:
This.. might actually kind of work??

Comments: 
Lesson learned: data should drive modelling.
